Improving the Replicability of Psychological Science Through Pedagogy

### 2017-06-23 paper/paper.Rmd
proposed reorg

# Results

## Pedagogical assessment

@@

@@

# Discussion

In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*. Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal. Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project. Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale, with implications both for replication pedagogy and for the practice of replication more broadly. We address each in turn.

Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015]. This kind of cross-class collaboration would require instructors to make class results more broadly discoverable. We can envision a number of possible avenues for this kind of sharing. For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines. Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/). Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible. For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.

@@

@@

One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators. This issue should be taken seriously by any instructor interested in doing replications in the classroom, but we believe it is not a major concern in the current case. First, our experimenters were graduate students, conducting other research in addition to their work in our class. Many of them will go on to publish in top journals (often alongside more senior collaborators), and this work will be treated on its merits, not on the basis of the experience level of the lead author. Indeed, evaluation on merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online. Second, the design of our course -- with multiple rounds of review by both graduate student teaching assistants and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages. In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research.

@@

@@

## Conclusions

Our results here demonstrate the practical possibility of performing replication research in the classroom. There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges. They are challenges for psychological science. We believe that the openness and transparency we pursued here as part of our pedagogical goals should be models not just for other classes but for future research more broadly.

>>>>

# Pedagogy: Results and Discussion

## Pedagogical Assessment

@@

# Empirical Findings: Results and Discussion

@@

@@

### Statistical Findings

@@

<!-- One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators. This issue should be taken seriously by any instructor interested in doing replications in the classroom, but we believe it is not a major concern in the current case. First, our experimenters were graduate students, conducting other research in addition to their work in our class. Many of them will go on to publish in top journals (often alongside more senior collaborators), and this work will be treated on its merits, not on the basis of the experience level of the lead author. Indeed, evaluation on merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online. Second, the design of our course -- with multiple rounds of review by both graduate student teaching assistants and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages. In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research. -->

@@

### Key Tests

@@

# General Discussion

In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*. Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal. Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project. Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].

This kind of cross-class collaboration would require instructors to make class results more broadly discoverable. We can envision a number of possible avenues for this kind of sharing. For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines. Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/). Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible. For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.

In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom. There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges. They are challenges for psychological science. We believe that the openness and transparency we pursued here as part of our pedagogical goals should be models not just for other classes but for future research more broadly.
